Timeliness of security updates for Android

### 2014-08-04 securityupdates.tex
Add script to update the graphs and update the graphs
Exploit rates are from 2012 and so not current
Use generated vulnerability table from os-version.py

Android relies on the Linux kernel to provide compartmentalisation and runs each app as a separate unix `user'.
The Linux kernel is a large piece of software and so there will always be new root exploits found in it~\cite{TODO}.
Manufacturers of Android devices have also added further root exploits when customising it~\cite{Grace2012}.
Between 36.7\%~\cite{Zhou2012b} and 40\%~\cite{Zhou2012a} of malware for Android contains root exploits.
While this shows that much Android malware does not need a root exploit to work, it can just request the relevant permissions and the user will grant them, a significant proportion does.
This malware is also more dangerous because while ordinary malware can be remotely removed by Google through the Play store, once a root exploit has been used there are no guarantees.

@@

\begin{table}
\centering
\begin{tabular}{c|c|c}
Vulnerability & Date known & How known \\
\hline
Exploid & 2010-07-15 & Public disclosure \\
Psneuter & 2011-01-06 & Public disclosure \\
Levitator & 2011-03-10 & CVE registered \\
ZergRush & 2011-10-06 & Exploit developed \\
APK duplicate file & 2013-02-18 & Fix committed \\
APK unsigned shorts & 2013-07-03 & Fix committed \\
% TODO this is an incomplete list, we need to add the rest here and in os-version.py
\end{tabular}
\caption{Root equivalent vulnerabilities in Android}
\label{tab:andvulns}
\end{table}

@@

The data from Device Analyzer (DA) we want to use to investigate the proportion of devices exposed to different vulnerabilities is the OS version.
Unfortunately there is no authoritative source of OS version information and so we cannot check directly whether our data is representative.
However Google has published API version information every month since December 2009 and we have collated this information.\footnote{\url{https://www.cl.cam.ac.uk/~drt24/android/versiondistribution/}}
While API versions are too coarse grained to use for security update detection they are closely related to OS versions and so if the DA data on API versions is similar to the Google Data on API versions then the DA data on OS versions should be representative.
Figure \ref{fig:play_api} shows the data Google and Figure \ref{fig:da_api} and they appear similar. %TODO we want a statistical metric to claim this strongly with.
\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{figures/play_norm_api_trunc}
 \caption{Google Play data on proportion of devices running different Android API versions}
 \label{fig:play_api}
\end{figure}
\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{figures/da_norm_api}
 \caption{Google Play data on proportion of devices running different Android API versions}
 \label{fig:da_api}
\end{figure}

This allows us to have confidence in the OS version information.
Figure \ref{fig:os} shows the raw data on the number of devices in the Device Analyzer data running different versions of Android each day.
It shows how old versions are gradually replaced by new ones, the long tail of devices which do not see updates to more recent versions and the fluctuation in the number of devices in the data.
Figure \ref{fig:norm_os} shows the normalised OS version distribution.
\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{figures/os}
 \caption{Android versions in Device Analyzer data over time}
 \label{fig:os}
\end{figure}
\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{figures/da_norm_os}
 \caption{Android versions in Device Analyzer data over time}
 \label{fig:norm_os}
\end{figure}

>>>>

Android relies on the Linux kernel to provide compartmentalisation and runs each app as a separate unix `user'.
The Linux kernel is a large piece of software and so there will always be new root exploits found in it~\cite{TODO}.
Manufacturers of Android devices have also added further root exploits when customising it~\cite{Grace2012}.
Between 36.7\%~\cite{Zhou2012b} and 40\%~\cite{Zhou2012a} of malware for Android contained root exploits in 2012.
While this shows that much Android malware does not need a root exploit to work, it can just request the relevant permissions and the user will grant them, a significant proportion does.
This malware is also more dangerous because while ordinary malware can be remotely removed by Google through the Play store, once a root exploit has been used there are no guarantees.

@@

\daTabAndVulns

@@

The data from Device Analyzer (DA) we want to use to investigate the proportion of devices exposed to different vulnerabilities is the OS version.
Unfortunately there is no authoritative source of OS version information and so we cannot check directly whether our data is representative.
However Google has published API version information every month since December 2009 and we have collated this information.\footnote{\url{https://www.cl.cam.ac.uk/~drt24/android/versiondistribution/}}
While API versions are too coarse grained to use for security update detection they are closely related to OS versions and so if the DA data on API versions is similar to the Google Data on API versions then the DA data on OS versions should be representative.
Figure \ref{fig:play_api} shows the data Google and Figure \ref{fig:da_api} and they appear similar. %TODO we want a statistical metric to claim this strongly with.
\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{figures/googleplayapi}
 \caption{Google Play data on proportion of devices running different Android API versions}
 \label{fig:play_api}
\end{figure}
\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{figures/da_norm_api}
 \caption{Google Play data on proportion of devices running different Android API versions}
 \label{fig:da_api}
\end{figure}

This allows us to have confidence in the OS version information.
Figure \ref{fig:os} shows the raw data on the number of devices in the Device Analyzer data running different versions of Android each day.
It shows how old versions are gradually replaced by new ones, the long tail of devices which do not see updates to more recent versions and the fluctuation in the number of devices in the data.
Figure \ref{fig:norm_os} shows the normalised OS version distribution.
\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{figures/da_os}
 \caption{Android versions in Device Analyzer data over time}
 \label{fig:os}
\end{figure}
\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{figures/da_norm_os}
 \caption{Android versions in Device Analyzer data over time}
 \label{fig:norm_os}
\end{figure}
